### 2015-06-27 reports/paper/introduction.tex
thesis update

\section{Outline}
We first discussed in Chapter II some prior relevant research and approaches in sound localization. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.

>>>>

\section{Outline}
We first discussed in Chapter II prior relevant research and approaches in sound localization. We also discussed various ways of combining past localization estimates for movement tracking. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.
